---
title: "SALAD Analyses in R"
author: "Lara Wieland"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
fig_caption: yes
---


This script 
- loads packages
- imports data
- recruits subscripts for 1) preparing aggregated variable names (prep_agg) and 2) transforming to long (longtowide_agg)
- reproduces Zsuzsi's ** analyses on the SALAD dataset** (descriptive only):

**Study design**
Within subject repeated measure: cond Stress(ST)/Control(CT)
Within subject measure: volat/phase (pre/rev/post) of Reversal Learning Task
Between subject measure: group Alcohol Disorder (AD)/Healthy Controls (HC)


```{r, include = FALSE}
knitr::opts_chunk$set(fig.width=15, fig.height=8, fig.path='Figs/')
```



### Load packages

```{r, include=FALSE}
rm(list = ls()) 

if (!require(ggplot2)) install.packages("ggplot2")
if (!require(readxl)) install.packages("readxl")
if (!require(tidyverse)) install.packages("tidyverse")
if (!require(psych)) install.packages("psych")
if (!require(car)) install.packages("car")
if (!require(lme4)) install.packages("lme4")
if (!require(reshape2)) install.packages("reshape2")
if (!require(ez)) install.packages("ez")
if (!require(broom)) install.packages("broom")
if (!require(strex)) install.packages("strex")
if (!require(nlme)) install.packages("nlme")
if (!require(lattice)) install.packages("lattice")
if (!require(tinytex)) install.packages('tinytex')
if (!require(purrr)) install.packages('purrr')
if (!require(knitr)) install.packages("knitr")
if (!require(kableExtra)) install.packages('kableExtra')
if (!require(stringr)) install.packages('stringr')
if (!require(hypr)) install.packages('hypr')
if (!require(schoRsch)) install.packages('schoRsch')
if (!require(hrbrthemes)) install.packages('hrbrthemes')
if (!require(emmeans)) install.packages('emmeans')
if (!require(psycho)) install.packages('psycho')
if (!require(gghalves)) install.packages('gghalves')
if (!require(sjPlot)) install.packages('sjPlot')
if (!require(sjmisc)) install.packages('sjmisc')
if (!require(effects)) install.packages('effects')
if (!require(sjstats)) install.packages('sjstats')
if (!require(cowplot)) install.packages('cowplot')
if (!require(ggpubr)) install.packages('ggpubr')
if (!require(foreign)) install.packages('foreign')
if (!require(lubridate)) install.packages('lubridate')
if (!require(chron)) install.packages('chron')

library("ggplot2")
library("readxl")
library("tidyverse")
library("psych")
library("car")
library("lme4")
library("reshape2")
library("ez")
library("broom")
library("strex")
library("nlme")
library("lattice")
library("tinytex")
library("purrr")
library("knitr")
library("kableExtra")
library("stringr")
library("hypr")
library('schoRsch')
library('hrbrthemes')
library('emmeans')
library('psycho')
library('gghalves')
library('sjPlot') #for plotting lmer and glmer mods
library('sjmisc') 
library('effects')
library('sjstats') #use for r2 functions
library('cowplot')
library("ggpubr")
library("foreign")
library("lubridate")
library("chron")

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
## NECESSARY TO RUN THIS FOR LATER RMANOVA ANALYSES (all markdowns in analyses folder)
source('preps/data_import.R')

```

```{r}
# plot underlying task structure for BCCN poster

state_rev <- c(1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1, 1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2, 2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2)

state_rev_2 <- replace(state_rev, state_rev==2, 0)

plot(state_rev_2,type = "o", col = "black", xlab = "Trial", ylab = "Outcome probability", main = "Contingencies")


```

### Demographics and NP - Descriptive Stats and T-Tests between groups
The dataset corresponds to sample 1 and includes `r nrow(dat)` subjects, of whom `r nrow(dat.AD)` are AD and `r nrow(dat.HC)` HC.
```{r, include=FALSE}

# These reproduced Zsuzsi's results: significant differences between groups in age and education, IQ_WST, num_forward, num_backward and DSST

by(dat$age, dat$group, mean)
# by(dat$age, dat$group, sd)
t.test(age ~ group, data=dat)

by(dat$education, dat$group, mean)
# by(dat$education, dat$group, sd)
t.test(education ~ group, data=dat)

by(dat$weight, dat$group, mean)
# by(dat$weight, dat$group, sd)
t.test(weight ~ group, data=dat)

# for IQ with dat_complete due to some NAs
#by(dat_complete$IQ_WST, dat_complete$group, mean)
# by(dat$IQ_WST, dat$group, sd)
#t.test(IQ_WST ~ group, data=dat_complete)

by(dat$num_forward, dat$group, mean)
# by(dat$num_forward, dat$group, sd)
t.test(num_forward ~ group, data=dat)

by(dat$num_backward, dat$group, mean)
# by(dat$num_backward, dat$group, sd)
t.test(num_backward ~ group, data=dat)

by(dat$tmt_a, dat$group, mean)
# by(dat$tmt_a, dat$group, sd)
t.test(tmt_a ~ group, data=dat)

by(dat$tmt_b, dat$group, mean)
# by(dat$tmt_b, dat$group, sd)
t.test(tmt_b ~ group, data=dat)

by(dat$dsst, dat$group, mean)
# by(dat$dsst, dat$group, sd)
t.test(dsst ~ group, data=dat)

mean.sum <- dat  %>% summarize(mean_age = mean(age))

options(knitr.kable.NA = "")
# then print it in a table using the kable command

kable(
  mean.
  sum,
  col.names = c("Groups")
) %>%
  kable_styling("striped") %>%
  footnote("HC = Healthy Controls, AD = Alcoholic Disorder", general_title = "Demographic and neuropsychological data")
#####

```
The groups are significantly different regarding age, education, IQ (num_forward, num_backward, DSST)

```{r, include=FALSE}
## NECESSARY TO RUN THIS FOR LATER RMANOVA ANALYSES (all markdowns in analyses folder)
source('preps/prep_agg.R')

```

```{r, include=FALSE}
## NECESSARY TO RUN THIS FOR LATER RMANOVA ANALYSES (all markdowns in analyses folder)
source('preps/longtowide_agg.R')

```

```{r, include=FALSE}
## transfer from wide to long format p_correct, reclassify variables, prepare for stats
# transfer them to long format as preparation for rmANOVA

longdat.correct <- melt(dat_all,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("sub_id", "group","order","age","IQ_WST","school_yrs"),
        # The source columns
    measure.vars=c("p_correct_pre_ST","p_correct_rev_ST","p_correct_post_ST","p_correct_pre_CT","p_correct_rev_CT","p_correct_post_CT"),
        # Name of the destination column that will identify the original
        # column that the measurement came from
    variable.name="phase",
    value.name="p_correct"
)

# use package strex to extract last number from sub_id and turn it into factor
longdat.correct$id <- str_last_number(longdat.correct$sub_id)
longdat.correct$id <- as.factor(longdat.correct$id)
longdat.correct$p_correct <- as.numeric(longdat.correct$p_correct)


longdat.correct <- longdat.correct %>% arrange(id)

longdat.correct <- longdat.correct %>% arrange(phase)

longdat.correct$volat1 <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))
longdat.correct$volat <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))
longdat.correct$volat2 <- as.numeric(longdat.correct$volat1)

levels(longdat.correct$volat)[levels(longdat.correct$volat)=="pre_ST"] <- "pre"
levels(longdat.correct$volat)[levels(longdat.correct$volat)=="rev_ST"] <- "rev"
levels(longdat.correct$volat)[levels(longdat.correct$volat)=="post_ST"] <- "post"

levels(longdat.correct$volat)[levels(longdat.correct$volat)=="pre_CT"] <- "pre"
levels(longdat.correct$volat)[levels(longdat.correct$volat)=="rev_CT"] <- "rev"
levels(longdat.correct$volat)[levels(longdat.correct$volat)=="post_CT"] <- "post"

longdat.correct <- longdat.correct %>% arrange(id)

# extract string ST or CT from phase strings and turn it into logical, then numeric
longdat.correct <- longdat.correct %>% mutate(cond = grepl("*CT",longdat.correct$phase)) 
longdat.correct <- longdat.correct %>% mutate(cond2 = longdat.correct$cond*1) %>% rename(cond = longdat.correct$cond2)

longdat.correct$group <- as.factor(longdat.correct$group) 
levels(longdat.correct$group) <- c('HC', 'AD')

longdat.correct$cond <- as.factor(longdat.correct$cond) 
levels(longdat.correct$cond) <- c('Stress', 'Control')
   
longdat.HC.correct <- longdat.correct %>% filter(longdat.correct$group == 'HC')
longdat.AD.correct <- longdat.correct %>% filter(longdat.correct$group == 'AD')

```


```{r, include=FALSE}
## transfer from wide to long format p_stay, reclassify variables, prepare for stats
# transfer them to long format as preparation for rmANOVA

longdat.stay <- melt(dat_all,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("sub_id", "group","order","age","school_yrs"),
        # The source columns
    measure.vars=c("p_stay_pre_ST","p_stay_rev_ST","p_stay_post_ST","p_stay_pre_CT","p_stay_rev_CT","p_stay_post_CT"),
        # Name of the destination column that will identify the original
        # column that the measurement came from
    variable.name="phase",
    value.name="p_stay"
)

# use package strex to extract last number from sub_id and turn it into factor
longdat.stay$id <- str_last_number(longdat.stay$sub_id)
longdat.stay$id <- as.factor(longdat.stay$id)
longdat.stay$p_stay <- as.numeric(longdat.stay$p_stay)

longdat.stay$volat1 <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))
longdat.stay$volat <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))

levels(longdat.stay$volat)[levels(longdat.stay$volat)=="pre_ST"] <- "pre"
levels(longdat.stay$volat)[levels(longdat.stay$volat)=="rev_ST"] <- "rev"
levels(longdat.stay$volat)[levels(longdat.stay$volat)=="post_ST"] <- "post"

levels(longdat.stay$volat)[levels(longdat.stay$volat)=="pre_CT"] <- "pre"
levels(longdat.stay$volat)[levels(longdat.stay$volat)=="rev_CT"] <- "rev"
levels(longdat.stay$volat)[levels(longdat.stay$volat)=="post_CT"] <- "post"

longdat.stay <- longdat.stay %>% arrange(id)

# extract string ST or CT from phase strings and turn it into logical, then numeric
longdat.stay <- longdat.stay %>% mutate(cond = grepl("*CT",longdat.stay$phase))
longdat.stay <- longdat.stay %>% mutate(cond2 = longdat.stay$cond*1) %>% rename(cond = longdat.stay$cond2)

longdat.stay$group <- as.factor(longdat.stay$group) 
levels(longdat.stay$group) <- c('HC', 'AD')

longdat.stay$cond <- as.factor(longdat.stay$cond) 
levels(longdat.stay$cond) <- c('Stress', 'Control')

```


```{r, include=FALSE}
## transfer from wide to long format p_sw, reclassify variables, prepare for stats
# transfer them to long format as preparation for rmANOVA

longdat.sw <- melt(dat_all,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("sub_id", "group","order","age","school_yrs"),
        # The source columns
    measure.vars=c("p_sw_pre_ST","p_sw_rev_ST","p_sw_post_ST","p_sw_pre_CT","p_sw_rev_CT","p_sw_post_CT"),
        # Name of the destination column that will identify the original
        # column that the measurement came from
    variable.name="phase",
    value.name="p_switch"
)

# use package strex to extract last number from sub_id and turn it into factor
longdat.sw$id <- str_last_number(longdat.sw$sub_id)
longdat.sw$id <- as.factor(longdat.sw$id)
longdat.sw$p_switch <- as.numeric(longdat.sw$p_switch)

longdat.sw$volat1 <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))
longdat.sw$volat <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))

levels(longdat.sw$volat)[levels(longdat.sw$volat)=="pre_ST"] <- "pre"
levels(longdat.sw$volat)[levels(longdat.sw$volat)=="rev_ST"] <- "rev"
levels(longdat.sw$volat)[levels(longdat.sw$volat)=="post_ST"] <- "post"

levels(longdat.sw$volat)[levels(longdat.sw$volat)=="pre_CT"] <- "pre"
levels(longdat.sw$volat)[levels(longdat.sw$volat)=="rev_CT"] <- "rev"
levels(longdat.sw$volat)[levels(longdat.sw$volat)=="post_CT"] <- "post"

longdat.sw <- longdat.sw %>% arrange(id)

# extract string ST or CT from phase strings and turn it into logical, then numeric
longdat.sw <- longdat.sw %>% mutate(cond = grepl("*CT",longdat.sw$phase))
longdat.sw <- longdat.sw %>% mutate(cond2 = longdat.sw$cond*1) %>% rename(cond = longdat.sw$cond2)

longdat.sw$group <- as.factor(longdat.sw$group) 
levels(longdat.sw$group) <- c('HC', 'AD')

longdat.sw$cond <- as.factor(longdat.sw$cond) 
levels(longdat.sw$cond) <- c('Stress', 'Control')

longdat.HC.sw <- longdat.sw %>% filter(longdat.sw$group == 'HC')

```


```{r, include=FALSE}
## transfer from wide to long format p_loseswitch, reclassify variables, prepare for stats
# transfer them to long format as preparation for rmANOVA

longdat.lswitch <- melt(dat_all,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("sub_id", "group","order","age","IQ_WST","school_yrs"),
        # The source columns
    measure.vars=c("p_l_sw_pre_ST","p_l_sw_rev_ST","p_l_sw_post_ST","p_l_sw_pre_CT","p_l_sw_rev_CT","p_l_sw_post_CT"),
        # Name of the destination column that will identify the original
        # column that the measurement came from
    variable.name="phase",
    value.name="p_lswitch"
)

# use package strex to extract last number from sub_id and turn it into factor
longdat.lswitch$id <- str_last_number(longdat.lswitch$sub_id)
longdat.lswitch$id <- as.factor(longdat.lswitch$id)
longdat.lswitch$p_lswitch <- as.numeric(longdat.lswitch$p_lswitch)


longdat.lswitch$volat1 <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))
longdat.lswitch$volat <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))
longdat.lswitch$volat2 <- as.numeric(longdat.lswitch$volat1)

levels(longdat.lswitch$volat)[levels(longdat.lswitch$volat)=="pre_ST"] <- "pre"
levels(longdat.lswitch$volat)[levels(longdat.lswitch$volat)=="rev_ST"] <- "rev"
levels(longdat.lswitch$volat)[levels(longdat.lswitch$volat)=="post_ST"] <- "post"

levels(longdat.lswitch$volat)[levels(longdat.lswitch$volat)=="pre_CT"] <- "pre"
levels(longdat.lswitch$volat)[levels(longdat.lswitch$volat)=="rev_CT"] <- "rev"
levels(longdat.lswitch$volat)[levels(longdat.lswitch$volat)=="post_CT"] <- "post"

longdat.lswitch <- longdat.lswitch %>% arrange(id)

# extract string ST or CT from phase strings and turn it into logical, then numeric
longdat.lswitch <- longdat.lswitch %>% mutate(cond = grepl("*CT",longdat.lswitch$phase))
longdat.lswitch <- longdat.lswitch %>% mutate(cond2 = longdat.lswitch$cond*1) %>% rename(cond = longdat.lswitch$cond2)

longdat.lswitch$group <- as.factor(longdat.lswitch$group) 
levels(longdat.lswitch$group) <- c('HC', 'AD')

longdat.lswitch$cond <- as.factor(longdat.lswitch$cond) 
levels(longdat.lswitch$cond) <- c('Stress', 'Control')

longdat.HC.lswitch <- longdat.lswitch %>% filter(longdat.lswitch$group == 'HC')
longdat.AD.lswitch <- longdat.lswitch %>% filter(longdat.lswitch$group == 'AD')

```


```{r, include=FALSE}
## transfer from wide to long format p_winstay, reclassify variables, prepare for stats
# transfer them to long format as preparation for rmANOVA

longdat.winstay <- melt(dat_all,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("sub_id", "group","order","age","IQ_WST","school_yrs"),
        # The source columns
    measure.vars=c("p_w_st_pre_ST","p_w_st_rev_ST","p_w_st_post_ST","p_w_st_pre_CT","p_w_st_rev_CT","p_w_st_post_CT"),
        # Name of the destination column that will identify the original
        # column that the measurement came from
    variable.name="phase",
    value.name="p_winstay"
)

# use package strex to extract last number from sub_id and turn it into factor
longdat.winstay$id <- str_last_number(longdat.winstay$sub_id)
longdat.winstay$id <- as.factor(longdat.winstay$id)
longdat.winstay$p_winstay <- as.numeric(longdat.winstay$p_winstay)

longdat.winstay$volat1 <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))
longdat.winstay$volat <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))
longdat.winstay$volat2 <- as.numeric(longdat.winstay$volat1)

levels(longdat.winstay$volat)[levels(longdat.winstay$volat)=="pre_ST"] <- "pre"
levels(longdat.winstay$volat)[levels(longdat.winstay$volat)=="rev_ST"] <- "rev"
levels(longdat.winstay$volat)[levels(longdat.winstay$volat)=="post_ST"] <- "post"

levels(longdat.winstay$volat)[levels(longdat.winstay$volat)=="pre_CT"] <- "pre"
levels(longdat.winstay$volat)[levels(longdat.winstay$volat)=="rev_CT"] <- "rev"
levels(longdat.winstay$volat)[levels(longdat.winstay$volat)=="post_CT"] <- "post"

longdat.winstay <- longdat.winstay %>% arrange(id)

# extract string ST or CT from phase strings and turn it into logical, then numeric
longdat.winstay <- longdat.winstay %>% mutate(cond = grepl("*CT",longdat.winstay$phase))
longdat.winstay <- longdat.winstay %>% mutate(cond2 = longdat.winstay$cond*1) %>% rename(cond = longdat.winstay$cond2)

longdat.winstay$group <- as.factor(longdat.winstay$group) 
levels(longdat.winstay$group) <- c('HC', 'AD')

longdat.winstay$cond <- as.factor(longdat.winstay$cond) 
levels(longdat.winstay$cond) <- c('Stress', 'Control')

longdat.HC.winstay <- longdat.winstay %>% filter(longdat.winstay$group == 'HC')
longdat.AD.winstay <- longdat.winstay %>% filter(longdat.winstay$group == 'AD')
```


```{r, include=FALSE}
## transfer from wide to long format p_RT, reclassify variables, prepare for stats
# transfer them to long format as preparation for rmANOVA

longdat.RT <- melt(dat_all,
# ID variables - all the variables to keep but not split apart on
    id.vars=c("sub_id", "group","order","age","school_yrs"),
# The source columns
    measure.vars=c("p_RT_pre_ST","p_RT_rev_ST","p_RT_post_ST","p_RT_pre_CT","p_RT_rev_CT","p_RT_post_CT"),
# Name of the destination column that will identify the original
# column that the measurement came from
    variable.name="phase",
    value.name="p_RT"
)

# use package strex to extract last number from sub_id and turn it into factor
longdat.RT$id <- str_last_number(longdat.RT$sub_id)
longdat.RT$id <- as.factor(longdat.RT$id)
longdat.RT$p_RT <- as.numeric(longdat.RT$p_RT)

longdat.RT <- longdat.RT %>% arrange(id)

longdat.RT <- longdat.RT %>% arrange(phase)

longdat.RT$volat1 <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))
longdat.RT$volat <- gl(6,nrow(dat_all),labels=c("pre_ST","rev_ST","post_ST","pre_CT","rev_CT","post_CT"))

levels(longdat.RT$volat)[levels(longdat.RT$volat)=="pre_ST"] <- "pre"
levels(longdat.RT$volat)[levels(longdat.RT$volat)=="rev_ST"] <- "rev"
levels(longdat.RT$volat)[levels(longdat.RT$volat)=="post_ST"] <- "post"

levels(longdat.RT$volat)[levels(longdat.RT$volat)=="pre_CT"] <- "pre"
levels(longdat.RT$volat)[levels(longdat.RT$volat)=="rev_CT"] <- "rev"
levels(longdat.RT$volat)[levels(longdat.RT$volat)=="post_CT"] <- "post"

longdat.RT <- longdat.RT %>% arrange(id)

# extract string ST or CT from phase strings and turn it into logical, then numeric
longdat.RT <- longdat.RT %>% mutate(cond = grepl("*CT",longdat.RT$phase))
longdat.RT <- longdat.RT %>% mutate(cond2 = longdat.RT$cond*1) %>% rename(cond = longdat.RT$cond2)

longdat.RT$group <- as.factor(longdat.RT$group) 
levels(longdat.RT$group) <- c('HC', 'AD')

longdat.RT$cond <- as.factor(longdat.RT$cond) 
levels(longdat.RT$cond) <- c('Stress', 'Control')

longdat.HC.RT <- longdat.RT %>% filter(longdat.RT$group == 'HC')
longdat.AD.RT <- longdat.RT %>% filter(longdat.RT$group == 'AD')

```

**Study design**
Within subject repeated measure: cond Stress(ST)/Control(CT)
Within subject measure: volat/phase (pre/rev/post) of Reversal Learning Task

### rmANOVA p_correct: 
1. for HC sample only main effect of volat, a non-significant interaction of volat * cond
2. for AD sample: here the volat * cond interaction stays significant as reflected in plot
3. for whole sample: main effect for volat and group, trendwise interaction effect
```{r}

# now ezANOVA can be filled with dv = p_correct, within-variables = volat(phase) and cond, between-variable = group and type 3 sums of squares

# first for HC only: 
res.HC.correct <- ezANOVA(longdat.HC.correct, p_correct, id, within = .(volat,cond), detailed = TRUE, type = 3)
res.HC.correct

# then for AD only: 
res.AD.correct <- ezANOVA(longdat.AD.correct, p_correct, id, within = .(volat,cond), detailed = TRUE, type = 3)
res.AD.correct

# now for whole sample without covariates
res.correct <- ezANOVA(longdat.correct, p_correct, id, within = .(volat,cond), between = .(group), detailed = TRUE, type = 3)
# now with school years and age as covariates
res.correct.wcov <- ezANOVA(longdat.correct, p_correct, id, within = .(volat,cond), between = .(group), between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)


# and make it look nicer
anova_out(res.correct.wcov)
anova_out(res.HC.correct)

# make a boxplot to take a look at distribution of p_correct group and phasewise
# panels show different groups
ggplot(longdat.correct, aes(x=phase, y=p_correct)) + geom_boxplot() + facet_grid(cols = vars(group))

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
fig1.bycond.pcorrect <- ezPlot(
   data = longdat.correct
   , dv = .(p_correct)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(group)
   , col = .(cond)
   , y_lab = "p_correct"
   , split_lab = "Group"
)

ggsave(fig1.bycond.pcorrect, filename = "perc_pcorrect_cond.png","jpg", "/Users/larawieland/Documents/Promotion/SALAD/plots")

fig1.bygroup.pcorrect <- ezPlot(
   data = longdat.correct
   , dv = .(p_correct)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(cond)
   , col = .(group)
   , y_lab = "p_correct"
   , split_lab = "Condition"
)


ggsave(fig1.bygroup.pcorrect, filename = "perc_pcorrect_group.png","jpg", "/Users/larawieland/Documents/Promotion/SALAD/plots")

# plot subjectwise trajectories across all volat phases in both conditions
xyplot(p_correct ~ volat1  | sub_id, groups=cond,auto.key = TRUE, data=longdat.correct, type='b')


```

## rmANOVA Model p_correct
```{r}

# predict p_correct only from intercept, 2 repeated measure factors (volat and cond2) are nested within participant (id)
basmod <- lme(p_correct ~ 1,data = longdat.correct, random = ~1|id/volat/cond2, method = "ML")

mod <- lme(p_correct ~ volat, random = ~1|id/volat/cond2,data = longdat.correct, method = "ML")

# main effects
groupmod <- update(basmod, .~. + group)
volatmod <- update(groupmod, .~. + volat)
condmod <- update(volatmod, .~. + cond2)

# 2-way interactions
group_volat <- update(condmod, .~. + group:volat)
group_cond <- update(group_volat, .~. + group:cond2)
volat_cond <- update(group_cond, .~. + volat:cond2)

# 3-way interactions
group_volat_cond <- update(volat_cond, .~. + group:volat:cond2)

# compare models with anova
anova(basmod, mod, groupmod, volatmod, condmod, group_volat, group_cond, volat_cond, group_volat_cond)

#plot for BCCN poster - line plot on main outcome variables + error bars
figure1 <- ggplot(longdat.HC.correct, aes(x = volat,y = p_correct, col = cond)) + stat_summary(fun = mean, geom = "point") + stat_summary(fun = mean, geom = "line", aes(group = cond)) + stat_summary(fun.data = mean_se, geom = "errorbar",width = 0.2, aes(group = cond)) + labs(y= "Percentage Correct", x = "Phase") +
  theme(
        panel.grid.major = element_line(colour = "lightgrey"),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = 'white'),
        )

ggsave(figure1, filename = "perc_correct_HC.png","jpg", "/Users/larawieland/Documents/Promotion/SALAD/plots")

```

## rmANOVA p_stay
```{r, include=FALSE}

# now ezANOVA can be filled with dv = p_stay, within-variable = cond, between-variable = group and type 3 sums of squares

res.stay <- ezANOVA(longdat.stay, p_stay, id, within = .(volat,cond), between = .(group), detailed = TRUE, type = 3)

# and make it look nicer
anova_out(res.stay)

# make a boxplot to take a look at distribution of p_stay group and phasewise
# panels show different groups
ggplot(longdat.stay, aes(x=phase, y=p_stay)) + geom_boxplot() + facet_grid(cols = vars(group))

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
ezPlot(
   data = longdat.stay
   , dv = .(p_stay)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(cond)
   , col = .(group)
   , y_lab = "p_stay"
   , split_lab = "Condition"
)

# plot subjectwise trajectories across all volat phases in both conditions
xyplot(p_stay ~ volat  | sub_id, groups=cond,auto.key = TRUE, data=longdat.stay, type='b')

```

## rmANOVA p_sw
```{r, include=FALSE}

# now ezANOVA can be filled with dv = p_switch, within-variable = cond, between-variable = group and type 2 sums of squares

# first for HC only
res.HC.sw <- ezANOVA(longdat.HC.sw, p_switch, id, within = .(volat,cond), detailed = TRUE, type = 3)

# now for whole sample
res.sw <- ezANOVA(longdat.sw, p_switch, id, within = .(volat,cond), between = .(group),between_covariates = .(school_yrs), detailed = TRUE, type =3)

# and make it look nicer
anova_out(res.sw)

# make a boxplot to take a look at distribution of p_switch group and phasewise
# panels show different groups
ggplot(longdat.sw, aes(x=phase, y=p_switch)) + geom_boxplot() + facet_grid(cols = vars(group))

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
ezPlot(
   data = longdat.sw
   , dv = .(p_switch)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(cond)
   , col = .(group)
   , y_lab = "p_switch"
   , split_lab = "Condition"
)

# plot subjectwise trajectories across all volat phases in both conditions
xyplot(p_switch ~ volat1  | sub_id, groups=cond,auto.key = TRUE, data=longdat.sw, type='b')

```

## rmANOVA p_lswitch
```{r, include=FALSE}

# now ezANOVA can be filled with dv = p_lswitch, within-variable = cond, between-variable = group and type 3 sums of squares

res.lswitch <- ezANOVA(longdat.lswitch, p_lswitch, id, within = .(volat,cond), between = .(group), detailed = TRUE, type = 3)

res.HC.lswitch <- ezANOVA(longdat.HC.lswitch, p_lswitch, id, within = .(volat,cond),between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)

res.lswitch.wcov <- ezANOVA(longdat.lswitch, p_lswitch, id, within = .(volat,cond), between = .(group), between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)

# and make it look nicer
anova_out(res.HC.lswitch)

# make a boxplot to take a look at distribution of p_lswitch group and phasewise, panels show different groups
ggplot(longdat.lswitch, aes(x=phase, y=p_lswitch)) + geom_boxplot() + facet_grid(group ~.)

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
fig3.bycond.plswitch <- ezPlot(
   data = longdat.lswitch
   , dv = .(p_lswitch)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(group)
   , col = .(cond)
   , y_lab = "p_lswitch"
   , split_lab = "Group"
)

ggsave(fig3.bycond.plswitch, filename = "perc_lswitch_cond.png","jpg", "/Users/larawieland/Documents/Promotion/SALAD/plots")

ave(longdat.HC.lswitch$p_lswitch,longdat.HC.correct$cond, FUN=sd)
tapply(longdat.HC.lswitch$p_lswitch, longdat.HC.correct$cond, sd)

#plot for BCCN poster - line plot on main outcome variables + error bars
figure3 <- ggplot(longdat.HC.lswitch, aes(x = volat,y = p_lswitch, col = cond)) + stat_summary(fun = mean, geom = "point") + stat_summary(fun = mean, geom = "line", aes(group = cond)) + stat_summary(fun.data = mean_se, geom = "errorbar",width = 0.2, aes(group = cond))+ labs(y= "Percentage Lose Switch", x = "Phase") +
    theme(
        panel.grid.major = element_line(colour = "#b7d8db"),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = 'white'),
        )

ggsave(figure3, filename = "perc_lswitch_HC.png","jpg", "/Users/larawieland/Documents/Promotion/SALAD/plots")

```

## rmANOVA p_winstay
1. for HC sample only main effect of volat, a non-significant interaction of volat*cond
2. for AD sample: neither a main effect of volat nor an interaction of volat * cond
3. for whole sample: no main effect of group, trendwise main effect of volat, significant volat * cond * group interaction
```{r}
# now ezANOVA can be filled with dv = p_correct, within-variables = volat(phase) and cond, between-variable = group and type 3 sums of squares

# first for HC only: only main effect for volat, a non-significant interaction for volat*cond
res.HC.winstay <- ezANOVA(longdat.HC.winstay, p_winstay, id, within = .(volat,cond),between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)
res.HC.winstay

# then for AD only: a non-significant main effect for volat and interaction for volat*cond
res.AD.winstay <- ezANOVA(longdat.AD.winstay, p_winstay, id, within = .(volat,cond), detailed = TRUE, type = 3)
res.AD.winstay

# now for the whole sample
res.winstay <- ezANOVA(longdat.winstay, p_winstay, id, within = .(volat,cond), between = .(group), detailed = TRUE, type = 3)
# now with school years and age as covariates
res.winstay.wcov <- ezANOVA(longdat.winstay, p_winstay, id, within = .(volat,cond), between = .(group), between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)


# and make it look nicer
anova_out(res.HC.winstay)
anova_out(res.winstay.wcov)

# make a boxplot to take a look at distribution of p_winstay group and phasewise
# panels show different groups
ggplot(longdat.sw, aes(x=phase, y=p_switch)) + geom_boxplot() + facet_grid(cols = vars(group))

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
fig1.bycond.pwinstay <- ezPlot(
   data = longdat.winstay
   , dv = .(p_winstay)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(group)
   , col = .(cond)
   , y_lab = "p_winstay"
   , split_lab = "Group"
)

ggsave(fig1.bycond.pwinstay, filename = "perc_wstay_cond.png","jpg", "/Users/larawieland/Documents/Promotion/SALAD/plots")

fig1.bygroup.pwinstay <- ezPlot(
   data = longdat.winstay
   , dv = .(p_winstay)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(cond)
   , col = .(group)
   , y_lab = "p_winstay"
   , split_lab = "Condition"
)

ggsave(fig1.bygroup.pwinstay, filename = "perc_wstay_group.png","jpg", "/Users/larawieland/Documents/Promotion/SALAD/plots")

# plot subjectwise trajectories across all volat phases in both conditions
xyplot(p_winstay ~ volat1  | sub_id, groups=cond,auto.key = TRUE, data=longdat.winstay, type='b')

```
## rmANOVA Model p_winstay
```{r}

# predict p_winstay only from intercept, 2 repeated measure factors (volat and cond2) are nested within participant (id)
basmod <- lme(p_winstay ~ 1,data = longdat.winstay, random = ~1|id/volat/cond2, method = "ML")

# 
mod <- lme(p_winstay ~ volat, random = ~1|id/volat/cond2,data = longdat.winstay, method = "ML")

# main effects
groupmod <- update(basmod, .~. + group)
volatmod <- update(groupmod, .~. + volat)
condmod <- update(volatmod, .~. + cond2)

# 2-way interactions
group_volat <- update(condmod, .~. + group:volat)
group_cond <- update(group_volat, .~. + group:cond2)
volat_cond <- update(group_cond, .~. + volat:cond2)

# 3-way interactions
group_volat_cond <- update(volat_cond, .~. + group:volat:cond2)

# compare models with anova
anova(basmod, mod, groupmod, volatmod, condmod, group_volat, group_cond, volat_cond, group_volat_cond)

#plot for BCCN poster - line plot on main outcome variables + error bars
figure2 <- ggplot(longdat.HC.winstay, aes(x = volat,y = p_winstay, col = cond)) + stat_summary(fun = mean, geom = "point") + stat_summary(fun = mean, geom = "line", aes(group = cond)) + stat_summary(fun.data = mean_se, geom = "errorbar",width = 0.2, aes(group = cond)) + labs(y= "Percentage Win Stay", x = "Phase") +
    theme(
        panel.grid.major = element_line(colour = "#b7d8db"),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = 'white'),
        labs(fill = "Dose (mg)")
    )

figure2 <- ggplot(longdat.HC.winstay, aes(x = volat,y = p_winstay, col = cond)) + stat_summary(fun = mean, geom = "point") + stat_summary(fun = mean, geom = "line", aes(group = cond)) + stat_summary(fun.data = mean_se, geom = "errorbar",width = 0.2, aes(group = cond))+ labs(y= "Percentage Win Stay", x = "Phase") +
    theme(
        panel.grid.major = element_line(colour = "#b7d8db"),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = 'white'),
        )

#ggsave(figure2, filename = "perc_wstay_HC.png","jpg", "/Users/larawieland/Documents/Promotion/SALAD/plots")


```

## rmANOVA Reaction Times
1. for HC sample no main effect of volat, a significant interaction of volat * cond
2. for AD sample: neither a main effect of volat nor an interaction of volat * cond
3. for whole sample: no main effect of group, no main effect of volat, significant volat * cond * group interaction
```{r}

# now ezANOVA can be filled with dv = p_RT, within-variables = volat(phase) and cond, between-variable = group and type 3 sums of squares

# first for HC only
res.HC.RT <- ezANOVA(longdat.HC.RT, p_RT, id, within = .(volat,cond), detailed = TRUE, type = 3)

# first for HC only
res.AD.RT <- ezANOVA(longdat.AD.RT, p_RT, id, within = .(volat,cond), detailed = TRUE, type = 3)

# now for whole sample
res.RT <- ezANOVA(longdat.RT, p_RT, id, within = .(volat,cond), between = .(group), between_covariates = .(age), detailed = TRUE, type = 3)

# and make it look nicer
anova_out(res.HC.RT)

# make a boxplot to take a look at distribution of RT group and phasewise, panels show different group
ggplot(longdat.RT, aes(x=phase, y=p_RT)) + geom_boxplot() + facet_grid(cols = vars(group))

p.agg.RT <- ezPlot(
   data = longdat.HC.RT
   , dv = .(p_RT)
   , wid = .(id)
   , within = .(volat,cond)
   , x = .(volat)
   , split = .(cond)
   , y_lab = "Reaction Times"
   , split_lab = "Condition"
)

p.agg.RT

xyplot(p_RT ~ volat1  | sub_id, groups=cond,auto.key = TRUE, data=longdat.RT, type='b')

```
## rmANOVA Model p_RT
```{r}

# predict p_winstay only from intercept, 2 repeated measure factors (volat and cond2) are nested within participant (id)
basmod <- lme(p_RT ~ 1,data = longdat.RT, random = ~1|id/volat/cond2, method = "ML")

# 
mod <- lme(p_RT ~ volat, random = ~1|id/volat/cond2,data = longdat.RT, method = "ML")

# main effects
groupmod <- update(basmod, .~. + group)
volatmod <- update(groupmod, .~. + volat)
condmod <- update(volatmod, .~. + cond2)

# 2-way interactions
group_volat <- update(condmod, .~. + group:volat)
group_cond <- update(group_volat, .~. + group:cond2)

# 3-way interactions
group_volat_cond <- update(group_cond, .~. + group:volat:cond2)

# compare models with anova
anova(basmod, mod, groupmod, volatmod, condmod, group_volat, group_cond, group_volat_cond)

ggplot(longdat.RT, aes(x = volat,y = p_RT, col = cond)) + stat_summary(fun = mean, geom = "point") + stat_summary(fun = mean, geom = "line", aes(group = cond)) + facet_grid(group ~.)

```


