---
title: "SALAD_modeling_prep"
author: "Lara Wieland"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
fig_caption: yes
---


### Load packages

```{r, include=FALSE}
rm(list = ls()) 

if (!require(ggplot2)) install.packages("ggplot2")
if (!require(ggplot2)) install.packages("readxl")
if (!require(tidyverse)) install.packages("tidyverse")
if (!require(psych)) install.packages("psych")
if (!require(reshape2)) install.packages("reshape2")
if (!require(car)) install.packages("car")
if (!require(car)) install.packages("lme4")
if (!require(ez)) install.packages("ez")
if (!require(strex)) install.packages("strex")
if (!require(nlme)) install.packages("nlme")
if (!require(lattice)) install.packages("lattice")
if (!require(tinytex)) install.packages('tinytex')
if (!require(tinytex)) install.packages('scales')

library("ggplot2")
library("readxl")
library("tidyverse")
library("psych")
library("car")
library("lme4")
library("reshape2")
library("ez")
library("strex")
library("nlme")
library("lattice")
library("tinytex")
library("scales")

```


## Remove outliers - find out which subjects performed < 55% p_correct
```{r}

# adapt path and data you want to import: operant_sample1 uses our extraction method, operant sample1_diff uses Zsuzsi's
setwd('/cloud/project/')
extrac_file <- "data_sum/operant_sample1.csv"
extrac_file_2 <- "data_sum/operant_sample1_diff.csv"

# import data, set missings (999) to NA and turn into tibble
my_data <- read_csv2(extrac_file,na = c("999", "NA"))

# remove outliers (according to < 55% p_correct in all trials or 1/3 phases)

dat.outlier.T1 <- my_data %>% filter(p_correct_T1 < .55)
dat.outlier.T2 <- my_data %>% filter(p_correct_T2 < .55)

```

```{r cars}

# attempts to write a function to detect outliers
is_outlier <- function(x) {
  return(x < .55)
}

# now print outlier labels (in this case the row number)
my_data$outlier <- my_data$outlier <- my_data$p_correct_T1 < .55

my_data <- my_data %>% mutate(group_level = factor(group, labels = c("HC", "AD")))
my_data$group <- as.factor(my_data$group_level)

my_data$p_correct_T1 <- as.numeric(my_data$p_correct_T1)
my_data$p_correct_T2 <- as.numeric(my_data$p_correct_T2)

p.1 <- ggplot(my_data, aes(group,p_correct_T1)) +
  geom_boxplot() +
  geom_text(aes(label = sub_id), size = 3, na.rm = TRUE, hjust = -0.3)

p.2 <- ggplot(my_data, aes(group,p_correct_T2)) +
  geom_boxplot() +
  geom_text(aes(label = sub_id), size = 3, na.rm = TRUE, hjust = -0.3)


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
