---
title: "SALAD Analyses in R"
author: "Lara Wieland"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
fig_caption: yes
---

This script (is not included in the manuscript):
1) loads necessary packages
2) recruits scripts from 'preps' for preparing aggregated variable names (prep_agg) and
3) transforming to long (widetolong_agg) and imports necessary datasets thereby
4) provides a chunk to reproduce the underlying task structure (not used, easier with Matlab)
5) descriptive analyses on age and education, neuropsychology (IQ_WST, num_backward and DSST)
6) adds repeated measures ANOVA for all main outcome variables + respective plots (only for HC, AD has been uncommented/not included); brief summary of result over every chunk
(a) p_correct
(b) p_stay
(c) p_switch
(d) p_lswitch
(e) p_winstay
(f) Reaction times

```{r, include = FALSE}
knitr::opts_chunk$set(fig.width=15, fig.height=8, fig.path='Figs/')
```

## 1) Load packages
```{r, include=FALSE}
rm(list = ls()) 

if (!require(ggplot2)) install.packages("ggplot2")
if (!require(ggpubr)) install.packages("ggpubr")
if (!require(tidyverse)) install.packages("tidyverse")
if (!require(psych)) install.packages("psych")
if (!require(car)) install.packages("car")
if (!require(lme4)) install.packages("lme4")
if (!require(reshape2)) install.packages("reshape2")
if (!require(ez)) install.packages("ez")
if (!require(broom)) install.packages("broom")
if (!require(strex)) install.packages("strex")
if (!require(nlme)) install.packages("nlme")
if (!require(lattice)) install.packages("lattice")
if (!require(tinytex)) install.packages('tinytex')
if (!require(reshape2)) install.packages('reshape2')
if (!require(sjmisc)) install.packages('sjmisc')
if (!require(schoRsch)) install.packages('schoRsch')

library("ggplot2")
library("ggpubr")
library("tidyverse")
library("psych")
library("car")
library("lme4")
library("reshape2")
library("ez")
library("broom")
library("strex")
library("nlme")
library("lattice")
library("tinytex")
library("sjmisc")
library("schoRsch")
library("gridExtra")
library("grid")
library("cowplot")


```

# 2)/3) Data import/Prep
```{r, include=FALSE}
## NECESSARY TO RUN THIS FIRST (if it does not work try uninstalling plyr or reshape2)
#detach("package:reshape2", unload=TRUE)
source("/cloud/project/preps/prep_agg.R")
source("/cloud/project/preps/widetolong_agg.R")


```

# 4) Task Structure
```{r}
# not included in manuscript
# plot underlying task structure for BCCN poster

state_rev <- c(1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1, 1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	1,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2, 2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2,	2)

state_rev_2 <- replace(state_rev, state_rev==2, 0)

plot(state_rev_2,type = "o", col = "black", xlab = "Trial", ylab = "Outcome probability", main = "Contingencies")


```

## 5) Demographics and NP - Descriptive Stats and T-Tests between groups
```{r, include=FALSE}
# partially included in manuscript
# These reproduced Zsuzsi's results: significant differences between groups in age and education, IQ_WST, num_forward, num_backward and DSST

by(dat_all$age, dat_all$group, mean)
# by(dat_all$age, dat_all$group, sd)
t.test(age ~ group, data=dat_all)

by(dat_all$education, dat_all$group, mean)
# by(dat_all$education, dat_all$group, sd)
t.test(education ~ group, data=dat_all)

by(dat_all$weight, dat_all$group, mean)
# by(dat_all$weight, dat_all$group, sd)
t.test(weight ~ group, data=dat_all)

# for IQ with dat_all_complete due to some NAs
#by(dat_all_complete$IQ_WST, dat_all_complete$group, mean)
# by(dat_all$IQ_WST, dat_all$group, sd)
#t.test(IQ_WST ~ group, data=dat_all_complete)

by(dat_all$num_forward, dat_all$group, mean)
# by(dat_all$num_forward, dat_all$group, sd)
t.test(num_forward ~ group, data=dat_all)

by(dat_all$num_backward, dat_all$group, mean)
# by(dat_all$num_backward, dat_all$group, sd)
t.test(num_backward ~ group, data=dat_all)

by(dat_all$tmt_a, dat_all$group, mean)
# by(dat_all$tmt_a, dat_all$group, sd)
t.test(tmt_a ~ group, data=dat_all)

by(dat_all$tmt_b, dat_all$group, mean)
# by(dat_all$tmt_b, dat_all$group, sd)
t.test(tmt_b ~ group, data=dat_all)

by(dat_all$dsst, dat_all$group, mean)
# by(dat_all$dsst, dat_all$group, sd)
t.test(dsst ~ group, data=dat_all)

sum_age <- data_all %>% summarise(MeanAge=mean(age,na.rm=T), sd=sd(age))
sum_school <- data_all %>% summarise(Meanschoolyears=mean(school_yrs,na.rm=T), sd=sd(school_yrs))

sum_iq <- data_all %>% summarise(MeanIQ=mean(IQ_WST,na.rm=T), sd=sd(IQ_WST,na.rm=T))

age_range <- range(data_all$age, na.rm=TRUE)


```


**Study design**
Within subject repeated measure: cond Stress(ST)/Control(CT)
Within subject measure: volat/phase (pre/rev/post) of Reversal Learning Task

## 6)(a) rmANOVA p_correct: 
1. for HC sample only main effect of volat, a non-significant interaction of volat * cond
# 2. for AD sample: here the volat * cond interaction stays significant as reflected in plot
3. for whole sample: main effect for volat and group, trendwise interaction effect
```{r,error=FALSE,warning=FALSE}
# not included in manuscript
# now ezANOVA can be filled with dv = p_correct, within-variables = volat(phase) and cond, between-variable = group and type 3 sums of squares

# first for HC only: 
res.HC.correct <- ezANOVA(longdat.HC.correct, p_correct, id, within = .(volat,cond), detailed = TRUE, type = 3)
res.HC.correct

# then for AD only: 
# res.AD.correct <- ezANOVA(longdat.AD.correct, p_correct, id, within = .(volat,cond), detailed = TRUE, type = 3)
# res.AD.correct

# now for whole sample without covariates
res.correct <- ezANOVA(longdat.correct, p_correct, id, within = .(volat,cond), between = .(group), detailed = TRUE, type = 3)
# now with school years and age as covariates
res.correct.wcov <- ezANOVA(longdat.correct, p_correct, id, within = .(volat,cond), between = .(group), between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)

# and make it look nicer
anova_out(res.correct.wcov)
anova_out(res.HC.correct)

# make a boxplot to take a look at distribution of p_correct group and phasewise
# panels show different groups
ggplot(longdat.correct, aes(x=phase, y=p_correct)) + geom_boxplot() + facet_grid(cols = vars(group))

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
fig1.bycond.pcorrect <- ezPlot(
   data = longdat.correct
   , dv = .(p_correct)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(group)
   , col = .(cond)
   , y_lab = "p_correct"
   , split_lab = "Group"
)

ggsave(fig1.bycond.pcorrect, filename = "perc_pcorrect_cond.png","jpg", "/cloud/project/plots/behav")

fig1.bygroup.pcorrect <- ezPlot(
   data = longdat.correct
   , dv = .(p_correct)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(cond)
   , col = .(group)
   , y_lab = "p_correct"
   , split_lab = "Condition"
)

ggsave(fig1.bygroup.pcorrect, filename = "perc_pcorrect_group.png","jpg", "/cloud/project/plots/behav")

# plot subjectwise trajectories across all volat phases in both conditions
xyplot(p_correct ~ volat1  | sub_id, groups=cond,auto.key = TRUE, data=longdat.correct, type='b')

#plot for BCCN poster - line plot on main outcome variables + error bars
figure1 <- ggplot(longdat.HC.correct, aes(x = volat,y = p_correct, col = cond)) + stat_summary(fun = mean, geom = "point") + stat_summary(fun = mean, geom = "line", aes(group = cond)) + stat_summary(fun.data = mean_se, geom = "errorbar",width = 0.2, aes(group = cond)) + labs(y= "Percentage Correct", x = "Phase") +
  theme(
        panel.grid.major = element_line(colour = "lightgrey"),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = 'white'),
        )
ggsave(figure1, filename = "perc_correct_HC.png","jpg", "/cloud/project/plots/behav")
```

## 6) (b) rmANOVA p_stay
```{r, include=FALSE,error=FALSE,warning=FALSE}
# not included in manuscript
# now ezANOVA can be filled with dv = p_stay, within-variable = cond, between-variable = group and type 3 sums of squares

res.stay <- ezANOVA(longdat.stay, p_stay, id, within = .(volat,cond), between = .(group), detailed = TRUE, type = 3)

# and make it look nicer
anova_out(res.stay)

# make a boxplot to take a look at distribution of p_stay group and phasewise
# panels show different groups
ggplot(longdat.stay, aes(x=phase, y=p_stay)) + geom_boxplot() + facet_grid(cols = vars(group))

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
ezPlot(
   data = longdat.stay
   , dv = .(p_stay)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(cond)
   , col = .(group)
   , y_lab = "p_stay"
   , split_lab = "Condition"
)

# plot subjectwise trajectories across all volat phases in both conditions
xyplot(p_stay ~ volat  | sub_id, groups=cond,auto.key = TRUE, data=longdat.stay, type='b')

```

## 6)(c) rmANOVA p_switch
```{r, include=FALSE,error=FALSE,warning=FALSE}
# not included in manuscript
# now ezANOVA can be filled with dv = p_switch, within-variable = cond, between-variable = group and type 2 sums of squares

# first for HC only
res.HC.sw <- ezANOVA(longdat.HC.sw, p_switch, id, within = .(volat,cond), detailed = TRUE, type = 3)

# now for whole sample
res.sw <- ezANOVA(longdat.sw, p_switch, id, within = .(volat,cond), between = .(group),between_covariates = .(school_yrs), detailed = TRUE, type =3)

# and make it look nicer
anova_out(res.HC.sw)

# make a boxplot to take a look at distribution of p_switch group and phasewise
# panels show different groups
ggplot(longdat.sw, aes(x=phase, y=p_switch)) + geom_boxplot() + facet_grid(cols = vars(group))

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
ezPlot(
   data = longdat.sw
   , dv = .(p_switch)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(cond)
   , col = .(group)
   , y_lab = "p_switch"
   , split_lab = "Condition"
)

# plot subjectwise trajectories across all volat phases in both conditions
xyplot(p_switch ~ volat1  | sub_id, groups=cond,auto.key = TRUE, data=longdat.sw, type='b')

```




## 6)(d) rmANOVA p_lswitch
```{r, include=FALSE,error=FALSE,warning=FALSE}
# not included in manuscript
# now ezANOVA can be filled with dv = p_lswitch, within-variable = cond, between-variable = group and type 3 sums of squares

res.lswitch <- ezANOVA(longdat.lswitch, p_lswitch, id, within = .(volat,cond), between = .(group), detailed = TRUE, type = 3)

res.HC.lswitch <- ezANOVA(longdat.HC.lswitch, p_lswitch, id, within = .(volat,cond),between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)

res.lswitch.wcov <- ezANOVA(longdat.lswitch, p_lswitch, id, within = .(volat,cond), between = .(group), between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)

# and make it look nicer
anova_out(res.HC.lswitch)

# make a boxplot to take a look at distribution of p_lswitch group and phasewise, panels show different groups
ggplot(longdat.lswitch, aes(x=phase, y=p_lswitch)) + geom_boxplot() + facet_grid(group ~.)

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
fig3.bycond.plswitch <- ezPlot(
   data = longdat.lswitch
   , dv = .(p_lswitch)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(group)
   , col = .(cond)
   , y_lab = "p_lswitch"
   , split_lab = "Group"
)

ggsave(fig3.bycond.plswitch, filename = "perc_lswitch_cond.png","jpg", "/cloud/project/plots/behav")

ave(longdat.HC.lswitch$p_lswitch,longdat.HC.correct$cond, FUN=sd)
tapply(longdat.HC.lswitch$p_lswitch, longdat.HC.correct$cond, sd)

#plot for BCCN poster - line plot on main outcome variables + error bars
figure3 <- ggplot(longdat.HC.lswitch, aes(x = volat,y = p_lswitch, col = cond)) + stat_summary(fun = mean, geom = "point") + stat_summary(fun = mean, geom = "line", aes(group = cond)) + stat_summary(fun.data = mean_se, geom = "errorbar",width = 0.2, aes(group = cond))+ labs(y= "Percentage Lose Switch", x = "Phase") +
    theme(
        panel.grid.major = element_line(colour = "#b7d8db"),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = 'white'),
        )

ggsave(figure3, filename = "perc_lswitch_HC.png","jpg", "/cloud/project/plots/behav")

```

## 6)(e) rmANOVA p_winstay
1. for HC sample only main effect of volat, a non-significant interaction of volat*cond
2. for AD sample: neither a main effect of volat nor an interaction of volat * cond
3. for whole sample: no main effect of group, trendwise main effect of volat, significant volat * cond * group interaction
```{r, include=FALSE,error=FALSE,warning=FALSE}
# not included in manuscript
# now ezANOVA can be filled with dv = p_correct, within-variables = volat(phase) and cond, between-variable = group and type 3 sums of squares

# first for HC only: only main effect for volat, a non-significant interaction for volat*cond
res.HC.winstay <- ezANOVA(longdat.HC.winstay, p_winstay, id, within = .(volat,cond),between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)
res.HC.winstay

# then for AD only: a non-significant main effect for volat and interaction for volat*cond
# res.AD.winstay <- ezANOVA(longdat.AD.winstay, p_winstay, id, within = .(volat,cond), detailed = TRUE, type = 3)
# res.AD.winstay

# now for the whole sample
res.winstay <- ezANOVA(longdat.winstay, p_winstay, id, within = .(volat,cond), between = .(group), detailed = TRUE, type = 3)
# now with school years and age as covariates
res.winstay.wcov <- ezANOVA(longdat.winstay, p_winstay, id, within = .(volat,cond), between = .(group), between_covariates = .(school_yrs,age), detailed = TRUE, type = 3)


# and make it look nicer
anova_out(res.HC.winstay)
anova_out(res.winstay.wcov)

# make a boxplot to take a look at distribution of p_winstay group and phasewise
# panels show different groups
ggplot(longdat.sw, aes(x=phase, y=p_switch)) + geom_boxplot() + facet_grid(cols = vars(group))

# plot rmANOVA in two panels (AD and HC) with within-factors volat (pre, rev, post) and cond(ST vs. CT)
fig1.bycond.pwinstay <- ezPlot(
   data = longdat.winstay
   , dv = .(p_winstay)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(group)
   , col = .(cond)
   , y_lab = "p_winstay"
   , split_lab = "Group"
)

ggsave(fig1.bycond.pwinstay, filename = "perc_wstay_cond.png","jpg", "/cloud/project/plots/behav")

fig1.bygroup.pwinstay <- ezPlot(
   data = longdat.winstay
   , dv = .(p_winstay)
   , wid = .(id)
   , within = .(volat,cond)
   , between = .(group)
   , x = .(volat)
   , split = .(cond)
   , col = .(group)
   , y_lab = "p_winstay"
   , split_lab = "Condition"
)

ggsave(fig1.bygroup.pwinstay, filename = "perc_wstay_group.png","jpg", "/cloud/project/plots/behav")

# plot subjectwise trajectories across all volat phases in both conditions
xyplot(p_winstay ~ volat1  | sub_id, groups=cond,auto.key = TRUE, data=longdat.winstay, type='b')

#plot for BCCN poster - line plot on main outcome variables + error bars

figure2 <- ggplot(longdat.HC.winstay, aes(x = volat,y = p_winstay, col = cond)) + stat_summary(fun = mean, geom = "point") + stat_summary(fun = mean, geom = "line", aes(group = cond)) + stat_summary(fun.data = mean_se, geom = "errorbar",width = 0.2, aes(group = cond))+ labs(y= "Percentage Win Stay", x = "Phase") +
    theme(
        panel.grid.major = element_line(colour = "#b7d8db"),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = 'white'),
        )
ggsave(figure2, filename = "perc_wstay_HC.png","jpg", "/cloud/project/plots/behav")

```

## 6) (f) rmANOVA Reaction Times
1. for HC sample no main effect of volat, a significant interaction of volat * cond
#2. for AD sample: neither a main effect of volat nor an interaction of volat * cond
3. for whole sample: no main effect of group, no main effect of volat, significant volat * cond * group interaction
```{r, include=FALSE,error=FALSE,warning=FALSE}
# not included in manuscript
# now ezANOVA can be filled with dv = p_RT, within-variables = volat(phase) and cond, between-variable = group and type 3 sums of squares

# first for HC only
res.HC.RT <- ezANOVA(longdat.HC.RT, p_RT, id, within = .(volat,cond), detailed = TRUE, type = 3)

# first for HC only
#res.AD.RT <- ezANOVA(longdat.AD.RT, p_RT, id, within = .(volat,cond), detailed = TRUE, type = 3)

# now for whole sample
res.RT <- ezANOVA(longdat.RT, p_RT, id, within = .(volat,cond), between = .(group), between_covariates = .(age), detailed = TRUE, type = 3)

# and make it look nicer
anova_out(res.HC.RT)

# make a boxplot to take a look at distribution of RT group and phasewise, panels show different group
ggplot(longdat.RT, aes(x=phase, y=p_RT)) + geom_boxplot() + facet_grid(cols = vars(group))

p.agg.RT <- ezPlot(
   data = longdat.HC.RT
   , dv = .(p_RT)
   , wid = .(id)
   , within = .(volat,cond)
   , x = .(volat)
   , split = .(cond)
   , y_lab = "Reaction Times"
   , split_lab = "Condition"
)
p.agg.RT

xyplot(p_RT ~ volat1  | sub_id, groups=cond,auto.key = TRUE, data=longdat.RT, type='b')
```

